\textbf{Access Control for Content Distribution Network Assets}

### 2016-05-23 tex/paper.tex
Changed some model stuff

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Action} & \textbf{Semantics} \\ \hline
        u, read(m, f)    & User \textit{u} reads \textit{f} from \textit{m}\\ \hline
        u, create(m, c)  & User \textit{u} creates \textit{m} in \textit{c}\\ \hline
        u, update(m, f)  & User \textit{u} updates \textit{f} with \textit{m}\\ \hline
        u, delete(o)     & User \textit{u} deletes \textit{o}\\ \hline
        u, snapshot(o)   & User \textit{u} takes a snapshot of \textit{o} \\ \hline
    \end{tabular}
\end{center}

@@

\vspace{1em}
The following predicates are used in several places and are therefore named \textit{*} to avoid
unnecessary repetition.
\begin{equation} \label{eq:predicate_rules}
    \inferrule
    {(\textbf{*}) \\ C \ni c \ni m \\ A[u,c]} 
    {}
\end{equation}

\vspace{1em}
\textbf{File Read}
\vspace{1em}
\begin{equation} \label{eq:fileread}
    \inferrule
    {(\textbf{*})} 
    {(C, F) \xrightarrow{u, read(m,f)} (C, F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{File Creation}
\vspace{1em}
\begin{equation} \label{eq:filecreate}
    \inferrule
    {C \ni c \\ A[u,c] \\ m \centernot \in c \\ \neg readOnly(c)} 
    {(C[c], F) \xrightarrow{u, create(m,c)} (C[c \cup \{m\}], F \cup \{m.file\})}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{File Update}
\vspace{1em}
\begin{equation} \label{eq:fileupdate}
    \inferrule
    {\textbf{*} \\ c' = c \cup \{m'\} \\ m' = \{id = m.id, file = f'\} \\ \neg readOnly(c)} 
    {(C[c \cup \{m\}], F) \xrightarrow{u, update(m, f')} ((C[c \cup \{m'\}], F \cup \{f'\}))}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Update}
\vspace{1em}
\begin{equation} \label{eq:contentupdate}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C[c \cup \{m\}], F) \xrightarrow{u, update(m, m')} ((C[c \cup \{m'\}], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\newpage
\textbf{Container Update}
\vspace{1em}
\begin{equation} \label{eq:containerupdate}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C[c], F) \xrightarrow{u, update(c, c')} (C[c'], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Copy}
\vspace{1em}
\begin{equation} \label{eq:copy}
    \inferrule
    {\textbf{*} \\ m' = \{id = \text{"fresh"}, file = m.file\} \\ \neg readOnly(c)}
    {(C[c \cup \{m\}], F) \xrightarrow{u, create(c, m')} (C[c \cup \{m, m'\}], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Deletion}
\vspace{1em}
\begin{equation} \label{eq:delete}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C[m], F) \xrightarrow{u, delete(m)} (C[], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Snapshot}
\vspace{1em}
\begin{equation} \label{eq:snapshot}
    \begin{split}
        [C', M'] := snapshot(tree) {}& \Implies \\
        \forall c \in tree, copy(c) \in {}& C' \\
        \forall m \in tree, copy(m) \in {}& M' \\
        \forall f \in tree, f \in {}& F
    \end{split}
\end{equation}

The non-trivial snapshot operation makes a deep-copy by traversing the full tree or sub-tree of
containers and content that is to be taken a snapshot of. As the snapshot operation is performed
upon a tree of objects it results in two new sets (C' and M') which are then added to C and M
respectively, the referred files in the content remain the same as before the snapshot.

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C, F) \xrightarrow{[C', M'] := u, snapshot(c)} (C[C' \cup M'], F)}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.

>>>>

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Action} & \textbf{Semantics} \\ \hline
        u, read(o)       & User \textit{u} reads \textit{o}\\ \hline
        u, create(m, c)  & User \textit{u} creates \textit{m} in \textit{c}\\ \hline
        u, update(m, f)  & User \textit{u} updates \textit{f} with \textit{m}\\ \hline
        u, delete(o)     & User \textit{u} deletes \textit{o}\\ \hline
        u, copy(o)       & User \textit{u} creates a copy of \textit{o}\\ \hline
        u, snapshot(o)   & User \textit{u} takes a snapshot of \textit{o} \\ \hline
    \end{tabular}
\end{center}

@@

\vspace{1em}
\textbf{File Read}
\vspace{1em}
\begin{equation} \label{eq:fileread}
    \inferrule
    {A[u,c] \\ C[c \cup \{m\}]} 
    {(C[c], F) \xrightarrow{u, read(f)} (C[c], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{File Creation}
\vspace{1em}
\begin{equation} \label{eq:filecreate}
    \inferrule
    {A[u,c] \\ m \centernot \in c \\ \neg readOnly(c)} 
    {(C[c], F) \xrightarrow{u, create(m,c)} (C[c \cup \{m\}], F \cup \{m.file\})}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{File Update}
\vspace{1em}
\begin{equation} \label{eq:fileupdate}
    \inferrule
    {A[u,c] \\ m' = \{id = m.id, file = f'\} \\ \neg readOnly(c)} 
    {(C[c \cup \{m\}], F) \xrightarrow{u, update(m, f')} ((C[c \cup \{m'\}], F \cup \{f'\}))}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Update}
\vspace{1em}
\begin{equation} \label{eq:contentupdate}
    \inferrule
    {A[u,c] \\ \neg readOnly(c)}
    {(C[c \cup \{m\}], F) \xrightarrow{u, update(m, m')} ((C[c \cup \{m'\}], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\newpage
\textbf{Container Update}
\vspace{1em}
\begin{equation} \label{eq:containerupdate}
    \inferrule
    {A[u,c] \\ \neg readOnly(c)}
    {(C[c], F) \xrightarrow{u, update(c, c')} (C[c'], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Copy}
\vspace{1em}
\begin{equation} \label{eq:copy}
    \inferrule
    {A[u,c] \\ m' = \{id = \text{"fresh"}, file = m.file\} \\ \neg readOnly(c)}
    {(C[c \cup \{m\}], F) \xrightarrow{u, copy(m)} (C[c \cup \{m, m'\}], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Deletion}
\vspace{1em}
\begin{equation} \label{eq:delete}
    \inferrule
    {A[u,c] \\ \neg readOnly(c)}
    {(C[c \cup \{m\}], F) \xrightarrow{u, delete(m)} (C[c \cup \{\}], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Snapshot}
\vspace{1em}
\begin{equation} \label{eq:snapshot}
    \begin{split}
        &snapshot(c) = \{c'.id = \textit{"fresh"}, snapshot(c') \mid c' \in c \} \cup \{ snapshot(m) \mid m \in c \}\\
        &snapshot({id = i, file = f }) = \{ id = \text{"fresh"}, file = f \} 
    \end{split}
\end{equation}

The snapshot operation makes a deep-copy by traversing the full tree or sub-tree of
containers and content that is to be taken a snapshot of. As the snapshot operation is performed
upon a tree of objects it results in two new sets (C' and M') which are then added to C and M
respectively, the referred files in the content remain the same as before the snapshot.

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {A[u,c] \\ \neg readOnly(c)}
    {(C[c], F) \xrightarrow{u, copy(c)} (C[c \cup snapshot(c)], F)}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.
